Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-17 paper.tex
psom debugging and provenance

        The pipeline manager is responsible for monitoring the state of the
pipeline and submitting jobs for execution. Its duties begin after the
initialization manager has completed execution. Jobs can be submitted by the
pipeline manager once all their dependencies have been satisfied. The
dependencies of a job are designated as met if there are none or when its parent jobs within the
dependency graph are tagged as \textit{finished}. In addition, a job is
considered to be successfully completely when all the dependencies of its
children jobs have been satisfied. Depending on the pipeline configuration,
there may be a limit to how many jobs can run in parallel. Once a job has
finished executing, an empty tag file is created with a filename containing the
final state in the logs folder. The pipeline manager continuously parses through
the logs folder in search of these state files to delete and update the history
file with the job state.

@@

        \subsection{limitations of PSOM}
    \section{SPM} 
        \subsection{summary} 
        \subsection{limitations of SPM} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

        The pipeline manager is responsible for monitoring the state of the
pipeline and submitting jobs for execution. Its duties begin after the
initialization manager has completed execution. Jobs can be submitted by the
pipeline manager once all their dependencies have been satisfied. The
dependencies of a job are designated as met if there are none or when its parent jobs within the
dependency graph are tagged as \textit{finished}. In addition, a job is
considered to be successfully completely when all the dependencies of its
children jobs have been satisfied. Depending on the pipeline configuration,
there may be a limit to how many jobs can run in parallel. Once a job has
finished executing, an empty tag file is created with a filename containing the
final state in the logs folder. The pipeline manager continuously parses through
the logs folder in search of these state files to delete and update the history
file with the job state. Both the pipeline manager and the jobs can be executed
within the current session, locally in a independent session, or in an
independent session on a cluster

@@

        The information stored in the logs folder is complete with details
allowing for both debugging and provenance. The logs folder contains six files:
1) PIPE\_history.txt, 2) PIPE\_jobs.mat, 3) PIPE\_status.mat, 4) PIPE\_logs.mat,
5) PIPE\_profile.mat and 6) PIPE.mat. PIPE\_history.txt includes the execution
history of the pipeline manager. PIPE\_jobs.mat and PIPE\_profile.mat are both
Matlab/Octave files containing each executed job as a Matlab variable. They
differ in that PIPE\_jobs.mat contains the latest executed jobs and can be used
to reexecute the pipeline at any moment in time and PIPE\_profile.mat contains
the execution time of each job \note{i think both can be used to reexecute
pipeline from scratch. Also unclear whether PIPE\_profile.mat contains more than
just latest jobs}. It is also possible to access any of the previously 
used parameters through PIPE\_jobs.mat. PIPE\_status.mat stores the status of each 
job as a string variable, whereas PIPE\_log.mat stores each job's log as a string 
variable. Job logs, as generated by the log manager, consist of a text copy of the 
execution, in addition to the user name, date, time and operating system used to 
execute the job. Finally, all configuration details are stored in PIPE.mat.

        \subsection{limitations of PSOM}
    \section{SPM} 
        \subsection{summary} 
        \subsection{limitations of SPM}
    \section{Nexflow}
        \subsection{summary}
    \section{OpenMOLE}
        \subsection{summary} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
